Smart Spreading Factor Assignment for LoRaWANs

### 2019-02-27 paper.tex
simlorafs doi reference

\section{Simulation Environment} \label{Simulation Environment}
A discrete event simulator is developed in Python to study the effects of different SF strategies in LoRaWANs. LoRaWAN SF simulation tool source code is available at GitHub \cite{simlorasf}. Simulation tool supports custom LoRaWAN topologies as well as randomly generated LoRaWAN topologies. Simulator can generate uniformly distributed circular shape network topology with following input parameters: radius (r) in meter (m), number of nodes and number of gateways. Global simulation input parameters are simulation duration in second (s), packet size in Byte (B), packet generation rate in packets per second (pps) and SF assignment method. With these inputs, the simulator produces total number of generated packets, number of successfully received packets, number of interfered packets, number of under sensitivity packets, network packet delivery ratio percentage (PDR), network throughput in bits per second (bps) and total transmit energy consumption in Joule (J). Simulator also produces prediction accuracy percentage and confusion matrix for machine learning schemes.

@@

For space constraints, we omit simulation results like network throughput, total transmit energy consumption and confusion matrices. We invite readers to experiment the simulation tool with the parameters they like \cite{simlorasf}.

>>>>

\section{Simulation Environment} \label{Simulation Environment}
A discrete event simulator is developed in Python to study the effects of different SF strategies in LoRaWANs. LoRaWAN SF simulation tool source code is available at GitHub \cite{tugrul_yatagan_2019_2579366}. Simulation tool supports custom LoRaWAN topologies as well as randomly generated LoRaWAN topologies. Simulator can generate uniformly distributed circular shape network topology with following input parameters: radius (r) in meter (m), number of nodes and number of gateways. Global simulation input parameters are simulation duration in second (s), packet size in Byte (B), packet generation rate in packets per second (pps) and SF assignment method. With these inputs, the simulator produces total number of generated packets, number of successfully received packets, number of interfered packets, number of under sensitivity packets, network packet delivery ratio percentage (PDR), network throughput in bits per second (bps) and total transmit energy consumption in Joule (J). Simulator also produces prediction accuracy percentage and confusion matrix for machine learning schemes.

@@

For space constraints, we omit simulation results like network throughput, total transmit energy consumption and confusion matrices. We invite readers to experiment the simulation tool with the parameters they like \cite{tugrul_yatagan_2019_2579366}.
